---
title: "{{PROJECT_ENV$titre}}"
author: 
  - {{PROJECT_ENV$cliniciens}}
  - {{paste(PROJECT_ENV$auteur, PROJECT_ENV$chefs, 'Department of Biostatistics and Medical Information, Saint-Louis hospital', sep = ', ')}}
date: "`r format(Sys.Date(), format = c('%d/%m/%Y'))`"
output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: sandstone
  officedown::rdocx_document:
    reference_docx: template_word_rmd.docx
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}
here::i_am("Scripts/05 - Report.Rmd")
library(here)
library(flextable)
library(tidyverse)
library(officer)
library(officedown)
library(knitr)
```

```{r chargement_bases, include=FALSE}
load(here("Data/base_v1.RData"))
load(here("Data/description.RData"))
# load(here("Data/analyse.RData"))
```


```{r}
NumTable <- 0
NumFigure <- 0
```


# Objectives

- ...
- Bullet list for the objectives.


# Statistical methods

Continuous variables are described with the median, 1^st^ and 3^rd^ quartiles and the range.
If the count is less than 4, only the median is presented.
Categorical variables are described by the counts with percentages.

The association of categorical variables were test using &chi;^2^ test/Fisher's exact test and continuous variables using Z-test/Student T-test/Wilcoxon's rank sum test.
All tests are bilateral with type I error rate of 5%.

Analyses are performed using R version X.X.X.

# Datamanagement

## Choices and corrections



## Questions on the base




## Potential discrepancies




## Already treated questions

<!-- <details> -->
<!--   <summary>Mail answers from ...</summary> -->
<!-- - retour 1 -->
<!-- - retour 2 -->
<!-- - ... -->
<!-- </details> -->


# Description







