---
title: "{{PROJECT_ENV$titre}}"
author: "{{paste(c(PROJECT_ENV$cliniciens, PROJECT_ENV$auteur, PROJECT_ENV$chefs), collapse = ", ")}}"
date: "`r format(Sys.Date(), format = c('%d/%m/%Y'))`"
output: 
  officedown::rdocx_document:
    reference_docx: template_word_rmd.docx
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}
here::i_am("Scripts/05 - Rapport.Rmd")
library(here)
library(flextable)
library(tidyverse)
library(officer)
library(officedown)
library(knitr)
```

```{r chargement_bases, include=FALSE}
load(here("Data/nom_base.RData"))
load(here("Data/tables_desc.RData"))
# load(here("Data/tables_analyses.RData"))
```



```{r}
block_toc()
```

\newpage

# Objectivess

- Bullet list for the objectives.


# Methods

Continuous variables are described with the median, 1^st^ and 3^rd^ quartiles and the range.
If the count is less than 4, 
Categorical variables are described by the counts with percentages.

The association of categorical variables were test using &chi;^2^ test/Fisher's exact test and continuous variables using Z-test/Student T-test/Wilcoxon's rank sum test.
All tests are bilateral with type I error rate of 5%.

\newpage

# Datamanagement

## Choices and corrections




## Discrepancies



\newpage

# Description







